---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# islet

<!-- badges: start -->
<!-- badges: end -->

The goal of islet is to help establish secure data pipelines for data cleaning and analytics, designed for teams analyzing patient outcome data. With Islet, you can easily clean and process sensitive patient data, while generating reports that track data irregularities and issues.

## Installation

You can install the development version of islet from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("shaunporwal/islet")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r load library}
library(islet)
```

```{r example 1}

# Simple Example, Default '&' Border
islet::make_banner(str_to_banner = 'analyze column from dataframe')
# Output Saved to Clipboard, Can Cmd+v or Ctrl+v to directly paste banner

```

```{r example 2}

# New Banner Border Example
islet::make_banner(str_to_banner = 'analyze column from dataframe',
                   banner_chr = '+')

```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
